---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scaleMultiply

<!-- badges: start -->
<!-- badges: end -->

The scaleMultiply package provides a utility function, `scale_and_multiply`, that scales a numeric vector to the range [0, 1] and then multiplies each element by a specified multiplier. This can be useful for data normalization and transformation tasks.

## Installation

You can install the development version of scaleMultiply from [GitHub](https://github.com/) with:

``` r
# install devtools if you haven't already
install.packages("devtools")
# use devtools to install this function packsage
devtools::install_github("stat545ubc-2024/scaleMultiply")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(scaleMultiply)

# Scale the vector to [0, 1] and multiply by 10
result <- scale_and_multiply(c(1, 2, 3, 4), multiplier = 10)
print(result)
```
In this example, the scale_and_multiply function takes a numeric vector c(1, 2, 3, 4), scales it to the range [0, 1], and then multiplies each element by the specified multiplier (10).


